Concurrent Programming with Harmony

### 2020-08-11 book/paper.tex
Latest

The implementation uses the \texttt{alloc} module for dynamic allocation
\index{dynamic allocation}%
of nodes in the list using \texttt{recAlloc} and \texttt{recFree}.
The read-only operation \texttt{lst\_contains} is wait\_free: it scans
through the list without having to obtain a lock.
Nonetheless, the implementation of the list is
\emph{linearizable}~\cite{HW90},
\index{linearizable}%
a strong notion of consistency that
makes it appear as if each of the operations executes atomically at
some point between their invocation and return.

@@

The \texttt{alloc} module
\index{alloc module}%
support thread-safe dynamic allocation of ``records.''
Each record has two fields: \texttt{.data} and \texttt{.next} that
can be used arbitrarily, although \texttt{.next} is intended to be
used as a pointer to another record.
There are just two methods:

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{recAlloc()} & allocate a record \\
\hline
\texttt{recFree($r$)} & free record $r$ \\
\hline
\end{tabular}
\vspace{1em}

The usage is similar to \texttt{malloc} and \texttt{free} in C.
\texttt{recAlloc} returns \texttt{None} when running out of memory.

>>>>

The implementation uses the \texttt{alloc} module for dynamic allocation
\index{dynamic allocation}%
of nodes in the list using \texttt{malloc} and \texttt{free}.
The read-only operation \texttt{lst\_contains} is wait\_free: it scans
through the list without having to obtain a lock.
Nonetheless, the implementation of the list is
\emph{linearizable}~\cite{HW90},
\index{linearizable}%
a strong notion of consistency that
makes it appear as if each of the operations executes atomically at
some point between their invocation and return.

@@

The \texttt{alloc} module
\index{alloc module}%
support thread-safe (but not interrupt-safe) dynamic allocation of
dictionaries.  There are just two methods:

\vspace{1em}
\begin{tabular}{|l|l|}
\hline
\texttt{malloc()} & allocate a dictionary \\
\hline
\texttt{free($r$)} & free an allocated dictionary $r$ \\
\hline
\end{tabular}
\vspace{1em}

The usage is similar to \texttt{malloc} and \texttt{free} in C.
\texttt{malloc}() returns \texttt{None} when running out of memory.
